A Test of the Frequency Independence Assumption of Power System Coefficients used in Geomagnetically Induced Current Estimates

### 2019-07-17 paper.tex

One-second-cadence electric and magnetic field measurements from Memanbetsu Magnetic Observatory (geodetic latitude: 43.910 N, geodetic longitude: 144.189 E) were obtained from the Japan Meteorological Agency data portal. The location of the observatory and substation are shown in Figure~\ref{map}.

@@

\acknowledgments
Magnetic and electric field measurements made at the Kakioka Magnetic Observatory was obtained from the Japan Meteorological Agency Data Portal \url{http://www.kakioka-jma.go.jp/obsdata/metadata/en}. We would like to thank the Hokkaido Electric Power Co. for the GIC measurements at the Memanbetsu substation and Shinichi Watari for communicating and preparing the GIC data and providing feedback on the manuscript. We also thank Ikuko Fujii for providing clarifications on the geoelectric instrument response, Trevor Gaunt and Emanuel Benabeau for review and comments on part (1) of Section 5, and Josh Rigler for substantial feedback and review.
%\clearpage

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/map.pdf}
\caption{Locations of measurement sites for GIC, at the Memanbetsu substation, and the geoelectric and geomagnetic field measurement site at Memambetsu Magnetic Observatory. The distance from the observatory to the substation is $\sim$9 km.}
\label{map}
\end{figure}

>>>>

One-second-cadence electric and magnetic field measurements from Memanbetsu Magnetic Observatory (geodetic latitude: 43.910$^o$ N, geodetic longitude: 144.189$^o$ E) were obtained from the Japan Meteorological Agency data portal. The location of the observatory and substation are shown in Figure~\ref{map}.

@@

\acknowledgments
Magnetic and electric field measurements made at the Kakioka Magnetic Observatory was obtained from the Japan Meteorological Agency Data Portal \url{http://www.kakioka-jma.go.jp/obsdata/metadata/en}. The geomagnetic coordinates in Figure~\ref{map} were computed using code from \url{https://www.ngdc.noaa.gov/geomag/geom_util/apex.shtml}. We would like to thank the Hokkaido Electric Power Co. for the GIC measurements at the Memanbetsu substation and Shinichi Watari for communicating and preparing the GIC data and providing feedback on the manuscript. We also thank Ikuko Fujii for providing clarifications on the geoelectric instrument response, Trevor Gaunt and Emanuel Benabeau for review and comments on part (1) of Section 5, and Josh Rigler for substantial feedback and review.
%\clearpage

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/map.pdf}
\caption{Locations of measurement sites for GIC, at the Memanbetsu substation, and the geoelectric and geomagnetic field measurement site at Memambetsu Magnetic Observatory. The red line corresponds to the path of the 187 kV power line. The distance from the observatory to the substation is $\sim$9 km; dotted lines are Apex geomagnetic latitudes \cite{Richmond1995} in 2015.}
\label{map}
\end{figure}
